Project Thesis/Report

### 2022-01-07 Gandhi_Project_Report/draft2.tex
Sortof done withCh.4 edits. Need to do a lot of work on 4.6

By generic we mean a residual set on a certain topology on appropriate spaces of functions (that we do not describe here) \textbf{(Cite)}.  %\ednote{How vague may one be in general by leaving things out?} 
By $C^2$, we make reference to a twice-differentiable function  with a continuous second derivative. In our scenario (and this remains important throughout) the input space $U$ is considered the attractor.

Below we reproduce Figure 1 from the supplementary material of \cite{manjunath2021universal}

@@

\vspace{-1cm}
\bibliographystyle{pnas-new}
\bibliography{pnas}

>>>>

By generic we mean a residual set on a certain topology on appropriate spaces of functions (that we do not describe here) \textbf{(Cite)}.  %\ednote{How vague may one be in general by leaving things out?} 
By $C^2$, we make reference to a twice-differentiable function  with a continuous second derivative. In our scenario (and this remains important throughout) the input space $U$ is considered the attractor.~\label{attractor_U}

Below we reproduce Figure 1 from \cite{Supp}.

@@

\vspace{-1cm}
% \bibliographystyle{pnas-new}
% \bibliography{pnas}
